Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

In terms of techniques, our main discovery is a result on the mathematical structure of the $k$-SJ problem. To facilitate the description of our finding, let us ``define'' the $k$-SJ problem at $k = 1$ as follows: the input is a set $R$ of $n$ rectangles in $\real^2$, and the objective is to list all the rectangles in $R$. Clearly, this 1-SJ problem can be trivially solved in $O(n)$ time. Our main technical contribution can now

>>>>

In terms of techniques, our primary contribution is a result on the mathematical structure of the $k$-SJ problem. To facilitate the description of our finding, let us ``define'' the $k$-SJ problem at $k = 1$ as follows: the input is a set $R$ of $n$ rectangles in $\real^2$, and the objective is to list all the rectangles in $R$. Clearly, this 1-SJ problem can be trivially solved in $O(n)$ time. Our main technical contribution can now be stated as:

\boxminipg{0.9\linewidth}{
    {\bf Main Discovery:} For $k \ge 3$, the $k$-SJ problem can be converted, in $O(n \log n)$ time, to 
}
